---
title: 'Classification'
author: 'Dataset res.PCA'
output:
  html_document: default
---
.

- - -

```{r, echo = FALSE}
library(FactoMineR)
load('C:/Users/alarc/Documents/Actuaría/Docencia/AMAT/R Intermedio/_Datos e Instalaciones/Music/Workspace.RData')
```

```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
drawn <-
c("Sobakasu.mp3", "Star Wars.mp3", "Hero's Come Back.mp3", "Superman.mp3", 
"Highway To Hell.mp3", "Don't Let Me Down.mp3", "The World.mp3", 
"Let It Be.mp3", "Get Back.mp3")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = 'tree', title = '')
```

**Figure 1.1 - Hierarchical tree.**

The classification made on individuals reveals 3 clusters.


```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = 'map', draw.tree = FALSE, title = '')
```

**Figure 1.2 - Ascending Hierarchical Classification of the individuals.**

The **cluster 1** is made of individuals such as *Don't Let Me Down.mp3*, *Get Back.mp3* and *Let It Be.mp3*. This group is characterized by :

- low values for the variables *LMean*, *LVar*, *LRan* and *LMed* (variables are sorted from the weakest).

The **cluster 2** is made of individuals such as *Star Wars.mp3*, *Superman.mp3*, *Hero's Come Back.mp3* and *The World.mp3*. This group is characterized by :

-  variables whose values do not differ significantly from the mean.

The **cluster 3** is made of individuals such as *Sobakasu.mp3* and *Highway To Hell.mp3*. This group is characterized by :

- high values for the variables *LRan*, *LMean*, *LMed* and *LVar* (variables are sorted from the strongest).

```{r, echo = FALSE, fig.align = 'center', fig.height = 5.5, fig.width = 5.5}
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.HCPC(res, choice = '3D.map', ind.names=FALSE, title = '')
```

**Figure 1.3 - Hierarchical tree on the factorial map.**

The hierarchical tree can be drawn on the factorial map with the individuals colored according to their clusters.


